MSDS 7333 Case Study 06

### 2017-06-21 MSDS7333_CaseStudy06_MBaldree_BBrock_TElkins_AKelly.Rmd
final review

### 1.2.1 <a id='SigStren'> Signal Strength Distributions</a>
Plot the signal strength distributions for each AP per angle for better understanding at location (X=2, Y=12). A more thorough analysis would examine the distributions at all locations points, but time did not permit this in-depth analysis.

@@

```{r}
# Let's focus on the fixed point (33,3)
df = subset(offline, posX == 33 & posY == 3 & !(mac %in% remainingAP), c(signal, angle, mac))
plotBoxplotSignalStrength(df)
# Figure 4 - Signal strength distribution for a point at the other end of the building
```
This plot is similar to the previous distribution but with no outliers. At this point we know signal strength is different for the two access points. We don't know if this will affect our prediction accuracy. Now, let us analyze the two AP's signal strength distribution over angles.

@@

#### Average Signal Strength Distributions
Plot the signal strength distribution for all locations through the average signal strength for all locations by angle. Summary statistics for all possible locations by angle were created.

@@

Table the test data to review the frequency for each angle and each coordinate. 
```{r}
online = readData("online.final.trace.txt", subMacs = macs)
online$posXY = paste(online$posX, online$posY, sep = "-")
length(unique(online$posXY))
tabonlineXYA = table(online$posXY, online$angle)
#output shows measurements were taken at all angles throughout the floor
tabonlineXYA
# Table 4 - Test data counts per location and angle
```
The above output shows that each angle has test data meaning we can test all angle for accuracy.

@@

  print(paste(ap, err))
}
# Table 6 - Accuracies for the various scenarios
```
The above results show that including both APs yielded a better prediction accuracy followed by keeping chosenAP and then rejectedAP. The author's choice to keep chosenAP was indeed better than rejectedAP, but keeping both of them is even better.

We next performed cross-validation with both APs to determine the best k. Three angles were used. Future work would include parameterization of the angles from 1 to 3 to determine the best m.

@@

<font color = "Red">provide some feel good about part 1. we concluded that keeping both APs yields better accuracy with a k-NN of 5 with 3 angles. We did not iterate of the angles to determine best parameter (arg!). The training data neighbors to the test data was determined by the signal strength distance and then the neighbors average X,Y was used to predict the test point location. </font>

>>>>

### 1.2.1 <a id='SigStren'> Signal Strength Distributions</a>
Plot the signal strength distributions for each AP per angle for better understanding at location (X=2, Y=12). A more thorough analysis would examine the distributions at all locations points, but time did not permit this in-depth analysis. Instead, we will later create a summary statistic to analyze.

@@

Next, we plot the signal strength distributions for each AP per angle for better understanding at location (X=33, Y=3).

```{r}
# Let's focus on the fixed point (33,3)
df = subset(offline, posX == 33 & posY == 3 & !(mac %in% remainingAP), c(signal, angle, mac))
plotBoxplotSignalStrength(df)
# Figure 4 - Signal strength distribution for a point at the other end of the building
```
This plot is similar to the previous distribution but with one outlier. At this point we know signal strength is different for the two access points. We do not know if this will affect our prediction accuracy. Now, let us analyze the two AP's signal strength distribution over angles.

@@

#### Average Signal Strength Distributions
Plot the signal strength distribution for all locations through the average signal strength for all locations by angle by creating a summary statistic for all possible locations.

@@

Table the test data to review the frequency for each angle and each coordinate. 
```{r}
online = readData("online.final.trace.txt", subMacs = macs)
online$posXY = paste(online$posX, online$posY, sep = "-")
length(unique(online$posXY))
tabonlineXYA = table(online$posXY, online$angle)
#output shows measurements were taken at all angles throughout the floor
tabonlineXYA
# Table 4 - Test data counts per location and angle
```
The above output shows that each angle has test data meaning we can test all angles for accuracy.

@@

  print(paste(ap, err))
}
# Table 6 - Accuracies for the various scenarios
```
The above results show that including both APs yielded a better prediction accuracy followed by keeping chosenAP and then rejectedAP. But was the difference significant or just do to chance? To answer this question, a null hypothesis should be performed.

Our null hypothesis is that all scenarios yield the same error. Our alternative hypothesis is that at least one scenario yields a different error from the others.

* Ho: None Error = ChosenAP Error = RejectedAP Error
* Ha: At least one scenario is different.

The next step is test our hypothesis with an ANOVA test. This step is left for future work. Therefore, we cannot reject Ho at this time.

We will proceed with our analysis with both APs and perform a cross-validation to determine the best k. Three angles were used. Future work would include parameterization of the angles from 1 to 3 to determine the best m.

@@

Our analysis of three scenarios that included both ChosenAP and RejectedAP and each exclused showed that there might be a potential gain from including both APs. Indeed the accuracy results showed including both APs yielded lower errors. However, this difference in errors was not analyzed for significance and was left for future work. A cross-validation for both APs scenario was performed to find optimal k. Analysis for optimal angle, m, was not peformed and left for future work.
